---
title: "Project G: Collaborating on Projects"
author: Kelley Lewis
output: html_notebook
---

*This project will require you to collaborate with some of your fellow students to complete a statistical analysis and report. Here are some of the tasks that you must accomplish.*

- Create a public GitHub repository with an RStudio project file (team leader)
- Put a description of the project in the README.md file (team leader)
- Email team members and Mike the repository address (team leader)
- Write a short introduction
- Provide a graphical display and descriptive statistics to compare groups
- Conduct an analysis of variance (ANOVA) for omnibus inference
- Check the conditions necessary for valid ANOVA inference
- Conduct a bootstrap for omnibus inference without needing conditions
- Construct Tukey pairwise confidence intervals (if appropriate)
- Write a conclusions section
- Assemble a complete knittable report (team leader)

*If you write any functions, put these in a **Functions** folder. Put data in a **Data** folder. These should be subfolders in your main project folder. Your finished notebook should be neat and organized. Save this notebook with your team name and **Project G** in the file name, rather than the report title. Leave the instructions in place and begin your report after the last horizontal line below. All team members will receive the same score for this project. (40 points possible)*

***

The *HSB2 Data* includes variables collected on a random sample of high school seniors. Conduct an analysis to compare performance on the test variable assigned to your team for the three socioeconomic groups. Include a graphical display and descriptive statistics. Also include an omnibus analysis that assumes valid conditions for parametric inference (ANOVA) as well as an omnibus analysis that does not assume these conditions (bootstrap). Construct pairwise Tukey confidence intervals, if appropriate.

***

```{r}
library(here)

library(boot)
library(ggplot2)

hsb2 <- read.csv(here("Data", "hsb2.csv"),
                      stringsAsFactors = FALSE)

```

```{r}
low_SES <- subset(hsb2, hsb2$ses == "1")

med_SES <- subset(hsb2, hsb2$ses == "2")

high_SES <- subset(hsb2, hsb2$ses == "3")
```

```{r include = FALSE}
# Custom function to find correlation
# between SES and Reading Score

corr.fun <- function(data, idx)
{
  df <- data[idx, ]
 
  # Find the spearman correlation between
  # the 4th (SES) and 7th (Read Score) columns of dataset
  c(cor(df[, 4], df[, 7], method = 'spearman'))
}
```

```{r include = FALSE}
# Setting the seed for
# reproducability of results
set.seed(42)
 
# Calling the boot function with the dataset
# our function and no. of rounds
bootstrap <- boot(hsb2, corr.fun, R = 10000)
 
# Display the result of boot function
bootstrap
```
```{r}
plot(bootstrap)
```
```{r include = FALSE}
# Function to find the
# bootstrap Confidence Intervals
boot.ci(boot.out = bootstrap,
        type = c("norm", "basic",
                 "perc", "bca"))
```


```{r}

### Low SES Bootstrap

# Initialize objects
mean_vector <- NULL
n <- length(low_SES$read)

# Take multiple samples (with replacement) and construct sampling
# distrbution of the mean

for (i in 1:10000) {
  the_sample <- sample(low_SES$read, n, replace = TRUE)
  mean_vector <- c(mean_vector, mean(the_sample))
}

# Sort the vector and cut off 2.5% on each end
mean_vector <- sort(mean_vector)
boot_int <- c(mean_vector[251], mean_vector[9750])

```

```{r}


### Medium SES Bootstrap

# Initialize objects
mean_vector2 <- NULL
n <- length(med_SES$read)

# Take multiple samples (with replacement) and construct sampling
# distrbution of the mean

for (i in 1:10000) {
  the_sample2 <- sample(med_SES$read, n, replace = TRUE)
  mean_vector2 <- c(mean_vector2, mean(the_sample2))
}

# Sort the vector and cut off 2.5% on each end
mean_vector2 <- sort(mean_vector2)
boot_int2 <- c(mean_vector2[251], mean_vector2[9750])

```


```{r}
### High SES Bootstrap

# Initialize objects
mean_vector3 <- NULL
n <- length(high_SES$read)

# Take multiple samples (with replacement) and construct sampling
# distrbution of the mean

for (i in 1:10000) {
  the_sample3 <- sample(high_SES$read, n, replace = TRUE)
  mean_vector3 <- c(mean_vector3, mean(the_sample3))
}

# Sort the vector and cut off 2.5% on each end
mean_vector3 <- sort(mean_vector3)
boot_int3 <- c(mean_vector3[251], mean_vector3[9750])

```


